### 2020-05-15 README.Rmd
fix: link to demo vignette
doc: add citation and refs to 2020 MSnbase2 preprint

To get an overview of the package, see the
[*MSnbase-demo*](https://lgatto.github.io/MSnbase/articles/MSnbase-demo.html) vignette. More
vignettes are available in the *Articles* tab.

@@

>>>>

To get an overview of the package, see the
[*MSnbase-demo*](http://lgatto.github.io/MSnbase/articles/v01-MSnbase-demo.html)
vignette. More vignettes are available in the *Articles* tab.

@@

> *`MSnbase`, efficient and elegant R-based processing and
> visualisation of raw mass spectrometry data*. Laurent Gatto,
> Sebastian Gibb, Johannes Rainer. bioRxiv 2020.04.29.067868; doi:
> https://doi.org/10.1101/2020.04.29.067868
